\documentclass[a4paper, 12pt]{article}
\usepackage[utf8]{inputenc}

\title{Assignment 01:Soft skills at the professional world }
\author{Ronald Mendez}
\date{23.04.2019}


\begin{document}
\maketitle
\begin{abstract}
    As a result of my experience in the professional field, I became aware of how important and necessary soft skills are, afterward was given the opportunity to learn them and put them in practice.
\end{abstract}
\section{Task 1: Soft Skills to be refined}
Today's world is a difficult place where to live, every activity has its portion of challenge and competitiveness, the professional area far from being an exception to this fact is the most notorious example of it. Then how can a person mark a difference in such a hostile environment, the answer to that question is something I have been cultivating the last years of my life.

During my bachelor's studies I was more concern about earning more knowledge, but lather during my professional life I realized that people with less preparation than me had better opportunities all because of their soft skills. That was reason enough for me to start working on aspects such as: being a better listener, transmit emotions while communicating no matter the way of communication, oratory, among others.

 When starting, I wasn't so sure about how good this could be, but later on in my last job, I was promoted to a position in which my technical knowledge was useful for about 10 percent of my job, while the rest should be accomplished by my ability to interact with people; hosting meetings, having project presentations with General managers, being related with people from every area of the company, suddenly became part of my everyday life.

the task wasn't easy, it took me a while to get used to it, but at the end I loved it, after a few months the job started to flow naturally out of me, but I would not like to be misunderstood here, I know this was just the beginning, but now I am really excited about keep making improvements on those skills. 

\section{Task 2: Perspective of the professional field}
\subsection{Task 2.A - Working opportunities of my interest}
\begin{itemize}
\item Software development Business Analyst (BA).
\item Project Manager (PM).
\item 4.0 Industry transformation leader.
\item Kaizen Leader.
\item Automation specialist.
\end{itemize}
\subsection{Task 2.B - Skills required}

In order to do a good job as a Business Analyst my management, conciliation, and requirement gathering skills need to be refined; while some others like facilitation and project obstacle removing need to be acquired, the mentioned interpersonal abilities are also necessary for a project manager who will also need to be a good decision maker, which is something I still have to work on.

On the other hand, 4.0 Industry transformation leader, Kaizen Leader and Automation specialist are positions generally associated to longer-term projects, with higher dose of leadership and team building which are skills still to be added to my toolbox.

\subsection{Task 2.C - Skill learning plan}

Being aware of the abilities required for a certain task is the first step, but not the hardest one on the road to become an accomplished professional. Skills like meeting facilitation, management, and especially leadership; come from a state of self-confidence, which is built of knowledge, experience, and planning. 

How this works; the knowledge leads to a clear vision of how things should be done an how the outcomes should look like in order to be considered as good, the experience helps to stay calm in difficult situations and also to be able to see possible solutions when facing problems, and finally a good plan is crucial in order to make quick and  good decisions.

Therefore, it is my intention now to build my leadership skills over those three pillars, and with that, it will come some others like decision making and team building, which in conclusion will make me capable of perform great in all of the previously mentioned positions.

\end{document}
